Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-18 cordillera-cycle.tex
Add geographic location of proxy records.

% tab:records
\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters used to
           prepare temperature offset time-series used to force the ice sheet
           model through the last 120\,kyr. $T_{[32;22]}$ refers to the
           mean temperature anomaly during the period -32 to~-22~kyr after
           scaling.}
  \label{tab:records}
  {\begin{tabular}{lcccc}
    \tophline
    Record & Proxy & Scaling factor & $T_{[32;22]}$ & Original reference\\
    \middlehline
    GRIP     & \chem{\delta^{18}O} & ?\% & -5.8{\degree}C
        & \citet{Dansgaard.etal.1993} \\
    NGRIP    & \chem{\delta^{18}O} & ?\% & -6.1{\degree}C
        & \citet{Andersen.etal.2004} \\
    EPICA    & \chem{\delta^{18}O} & ?\% & -5.6{\degree}C
        & \citet{Jouzel.etal.2007} \\
    Vostok   & \chem{\delta^{18}O} & ?\% & -5.6{\degree}C
        & \citet{Petit.etal.1999} \\
    ODP~1012 & \chem{U^{K'}_{37}}  & ?\% & -5.8{\degree}C
        & \citet{Herbert.etal.2001} \\
    ODP~1020 & \chem{U^{K'}_{37}}  & ?\% & -5.8{\degree}C
        & \citet{Herbert.etal.2001} \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

>>>>

% tab:records
\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters used to
           prepare temperature offset time-series used to force the ice sheet
           model through the last 120\,kyr. $f$ corresponds to the scaling
           factor used and $T_{[32;22]}$ refers to the mean temperature anomaly
           during the period -32 to~-22~kyr after scaling.}
  \label{tab:records}
  {\begin{tabular}{lccccccl}
    \tophline
    Record & Lat. & Lon. & Elev. & Proxy & $f$ & $T_{[32;22]}$
           & Original reference\\
    \middlehline
    GRIP     &  72{\degree} 35' N  % 72.58 (decimal)
             &  37{\degree} 38' W  % 37.64 (decimal)
             & 3238\,m
             & \chem{\delta^{18}O}
             & 0.35 & -5.8{\degree}C  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

    NGRIP    &  75{\degree} 06' N  % 75.10
             &  42{\degree} 19' W  % 42.32
             & 2917\,m
             & \chem{\delta^{18}O}
             & 0.22 & -6.1{\degree}C  % -26.7098
             & \citet{Andersen.etal.2004} \\

    EPICA    &  75{\degree} 06' S  % 75.1
             & 123{\degree} 21' E  % 123.35
             & 3233\,m
             & \chem{\delta^{18}O}
             & 0.60 & -5.6{\degree}C  % -9.2055
             & \citet{Jouzel.etal.2007} \\

    Vostok   &  78{\degree} 28' S  % 78.8
             & 106{\degree} 50' E  % 106.8
             & 3488\,m
             & \chem{\delta^{18}O}
             & 0.70 & -5.6{\degree}C  % -7.9550
             & \citet{Petit.etal.1999} \\

    ODP~1012 &  32{\degree} 17' N
             & 118{\degree} 23' W
             & -1772\,m
             & \chem{U^{K'}_{37}}
             & 1.53 & -5.8{\degree}C  % -3.7889
             & \citet{Herbert.etal.2001} \\

    ODP~1020 &  41{\degree} 00' N
             & 126{\degree} 26' W
             & -3038\,m
             & \chem{U^{K'}_{37}}
             & 1.16 & -5.8{\degree}C  % -5.0000
             & \citet{Herbert.etal.2001} \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}
